Dynamic Transition Analysis with TIMES

### 2020-09-16 doc/2020-03-paper/Appendix.tex
minor edits
Former-commit-id: d6edc638a459eb9c40c1e86d88715c92474ee6ee
Former-commit-id: 53262b3a3a1fdbe1e41f4720e63dfa8eda7f585e
added pws capacity factor
Former-commit-id: ef1132612ec949e6d38c329589843b014e6f8087
Former-commit-id: 23dd5676499da8d401ff9bfab0308be51139a606
methodology minor corrections
Former-commit-id: bb5704f9059dd6be7778d735aea63348d7012923
Former-commit-id: 216117c713e2cf9f6af0e1b9954b547e6853bd45
added final data references
Former-commit-id: 8768788b73a32289546225ccaa7e74028a3a5111
Former-commit-id: e84176721cdfaa57f6b7c10d5e92fde1a81dda1d

\section{Data and assumptions for scenarios} \label{Appendix}
\begin{table}[!ht]
	\caption{Data for initial condition.}
	\vspace{0.1in}
	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
		\hline
\textbf{Technology} & \textbf{\gls{lcoe}} & \textbf{Emission} & \textbf{Year of total}\\
  & (USD/kWh) & \textbf{Coefficients} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
\hline
Coal & 0.06 & 943 & 2030 \\
\gls{lng} & 0.08 & 599 & 2030 \\
Oil & 0.39 & 738 & 2030 \\
Nuclear & 0.11 & 21 & 2069 \\
Hydro & 0.05 & 11 & N.A. \\
Geothermal & 0.12 & 13 & N.A. \\
Wind & 0.11 & 25 & 2040 \\
Solar & 0.15 & 37 & 2040 \\
\hline 
\end{tabularx}
\label{init-eco}
\end{table}

@@

\begin{table}[!ht]
	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.08\textwidth} p{0.35\textwidth} p{0.35\textwidth} p{0.15\textwidth}}
		\hline
\textbf{Year} & \textbf{Model Emissions} & \textbf{Actual Emissions} & \textbf{Error} \\
  & Mt CO$_2$-eq. & Mt CO$_2$-eq. &  \\
\hline
2013 & 603.62 & 592.4 & 1.89 \% \\
2014 & 582.27 & 572.6 & 1.69 \% \\
2015 & 572.53 & 560.3 & 2.18 \% \\
2016 & 565.94 & 552.8 & 2.38 \% \\
\hline 
	\end{tabularx}
\label{ic-co2}
\end{table}

\begin{landscape}
\begin{longtable}{ |*{8}{c|} }
\caption{Economic data for modelled technologies.}\\
\hline
\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity Factor/} & \textbf{Emission} & \textbf{Year} \\
\textbf{name} & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
 & MUSD/GW & MUSD/GW & MUSD/GWh & Years  &  & gCO$_2$/kWh  &  \\
\hline
\endhead  % header material
\hline
\endfoot  % footer material
\hline
\endlastfoot
\gls{USC} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
\gls{lng} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
Nuclear & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
 & 1446 (2025) &  &  &  &  & 87(2050) &  \\
Solar & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
 & 615(2050) & & & & & &  \\
Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
 & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
 & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
 & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
LNG-CCS(90\%) & 2626(2022) & 27.484 & 0.0494 & 30 & CF=0.12-0.4(2017) & 94 & 2022 \\
 & 1422(2050) &  & &  &  &  & \\
USC-CCS(90\%) & 5252(2023) & 59 & 0.078 & 40 & CF=0.27-0.32(2017) & 236.5 & 2023 \\
 & 4091(2050) &  &  &  &  &  & \\
Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
  & 600(2050) &  &  &  &Eff=0.3(2030)  & 13(2040) &  \\
\gls{AEC} & 1500(2022) & 8 & 0.0004 & 11(CF=0.9) & Eff=0.7 & 1.29 & 2022\\
 & 850(2030) &  &  &  &  & &  \\
\gls{PEMEC} & 3500(2022) & 8 & 0.0004 & 7 (2022)(CF=0.9) & Eff=0.75(2022) & 8.7(2022) & 2022\\
 & 1500(2030) &  & 11(2050)  &  & Eff=0.82(2030) & 0.456(2050)  &  \\
 & 400(2050) &  &  &  & &  &  \\
\gls{SOEC} & 6000(2030) & 8 & 0.0004 & 2 (2030)(CF=0.9) & Eff=0.9 & 5.4(2030) & 2030\\
 & 1000(2050) &  &  & 7 (2050) &  & 1.08(2050) & \\
 & 400(2070) &  &  & 11 (2070) &  & 0.72(2070) & \\
Gas Reforming & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 356.6 & 2022\\
Gas Reforming-CCS(70\%) & 1200 & 8 & 0.065 & 30 & Eff=0.56 & 179 & 2022\\
\gls{PEMFC} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.49 & 1.087(2022) & 2022\\
 & 4000(2030) &  &  &  &  & 0.65(2030) &  \\
 & 3000(2035) &  &  &  &  &  &  \\
\gls{SOFC} & 7399(2030) & 30.65 & 0.59 & 10 (CF=0.9) & Eff=0.7 & 2.11(2030) & 2030\\
 & 4000(2035) &  &  &  &  & 1.27(2040) &  \\
 & 3000(2040) &  &  &  &  & &  \\
\gls{PWS} & 14706  & 236.5 & 0 & 20(CF=0.9) & Eff=0.15(2050) & Unknown & 2050
\label{eco}
\end{longtable}
\end{landscape}

\begin{table}[!ht]
	\caption{Capacity limits.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth} }
		\hline
\textbf{Technology} & \textbf{Net Capacity} \textbf{Limit} (GW)\\
\hline
Photovoltaic & 332 \\
Onshore wind & 180 \\
Offshore wind (fixed) & 130 \\
Offshore wind (floating) & 260 \\
Nuclear & 50 (Scenarios 3 \& 4) \\
 & 100 (Scenario 2) \\
\gls{PWS} & 100 (Scenario 5) \\
\hline 
\end{tabularx}
\label{caplim}
\end{table}

\begin{table}[!ht]
%\begin{minipage}{\textwidth} 
	\caption{Capacity growth rates.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
		\hline
\textbf{Technology} & \textbf{Max. Annual} \\
  & \textbf{Growth Rate}   \\
\hline
Nuclear (2027 onwards) & +5 reactors \\
Solar and Emerging Solar & 40\%  \\
Onshore Wind & 25\% \\
Offshore Wind(Fixed) & 20\% \\
Offshore Wind(Floating) & 20\% \\
Li-ion Storage & 30\% \\
Natural Gas &  50\% \\
\gls{USC} & 50\% \\
All emerging technologies & 40\% (Years 1-5) \\
& 60\% (Years 6-10) \\
 & 40\% (Years 11-15) \\
 & 30\% (Years 16-) \\
\hline 
\end{tabularx}
\label{growrate}
%\end{minipage}
\end{table}

>>>>

\section{Data and assumptions for scenarios} \label{Appendix}

\begin{table}[!ht]
	\caption{Data for initial condition.}
	\vspace{0.1in}
	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
		\hline
\textbf{Technology} & \textbf{\gls{lcoe}} \cite{lazard_lazards_2016} & \textbf{Emission} & \textbf{Year of total}\\
  & (USD/kWh) & \textbf{Coefficients} \cite{the_federation_of_electric_power_companies_of_japan_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
\hline
Coal & 0.06 & 943 & 2030 \\
\gls{lng} & 0.08 & 599 & 2030 \\
Oil & 0.39 & 738 & 2030 \\
Nuclear & 0.11 & 21 & 2069 \\
Hydro & 0.05 & 11 & N.A. \\
Geothermal & 0.12 & 13 & N.A. \\
Wind & 0.11 & 25 & 2040 \\
Solar & 0.15 & 37 & 2040 \\
\hline 
\end{tabularx}
\label{init-eco}
\end{table}

@@

\begin{table}[!ht]
	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.08\textwidth} p{0.35\textwidth} p{0.35\textwidth} p{0.15\textwidth}}
		\hline
\textbf{Year} & \textbf{Model Emissions} & \textbf{Actual Emissions} & \textbf{Error} \\
  & Mt CO$_2$-eq. & Mt CO$_2$-eq. &  \\
\hline
2013 & 603.62 & 592.4 & 1.89 \% \\
2014 & 582.27 & 572.6 & 1.69 \% \\
2015 & 572.53 & 560.3 & 2.18 \% \\
2016 & 565.94 & 552.8 & 2.38 \% \\
\hline 
	\end{tabularx}
\label{ic-co2}
\end{table}

\begin{landscape}
\begin{longtable}{ |*{8}{c|} }
\caption{Economic data for modelled technologies.}\\
\hline
\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity Factor/} & \textbf{Emission} & \textbf{Year} \\
 & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
 & MUSD/GW & MUSD/GW & MUSD/GWh & Years  &  & gCO$_2$/kWh  &  \\
\hline
\endhead  % header material
\hline
\endfoot  % footer material
\hline
\endlastfoot
\gls{USC} \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
\gls{lng}\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
Nuclear \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\
Li-ion Storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\
 & 1446 (2025) &  &  &  &  & 87(2050) &  \\
Solar \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
 & 615(2050) & & & & & &  \\
Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\
Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\
Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\
LNG-CCS(90\%) & 2626(2022) & 27.484 & 0.0494 & 30 & CF=0.12-0.4(2017) & 94 & 2022 \\
 \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1422(2050) &  & &  &  &  & \\
USC-CCS(90\%) & 5252(2023) & 59 & 0.078 & 40 & CF=0.27-0.32(2017) & 236.5 & 2023 \\
 \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 4091(2050) &  &  &  &  &  & \\
Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
 \cite{irena_solar_2012,peng_review_2013} & 600(2050) &  &  &  &Eff=0.3(2030)  & 13(2040) &  \\
\gls{AEC}  & 1500(2022) & 8 & 0.0004 & 11(CF=0.9) & Eff=0.7 & 1.29 & 2022\\
\cite{iea_technology_2015, bhandari_life_2014, cetinkaya_life_2012, burkhardt_hydrogen_2016} & 850(2030) &  &  &  &  & &  \\
\gls{PEMEC} & 3500(2022) & 8 & 0.0004 & 7 (2022)(CF=0.9) & Eff=0.75(2022) & 8.7(2022) & 2022\\
\cite{iea_technology_2015, bareis_life_2019, carmo_comprehensive_2013,ayers_research_2010,siracusano_influence_2017,schmidt_future_2017,mayyas_manufacturing_2019} & 1500(2030) &  & 11(2050)  &  & Eff=0.82(2030) & 0.456(2050)  &  \\
 & 400(2050) &  &  &  & &  &  \\
\gls{SOEC} & 6000(2030) & 8 & 0.0004 & 2 (2030)(CF=0.9) & Eff=0.9 & 5.4(2030) & 2030\\
\cite{iea_technology_2015,schmidt_future_2017,hafele_life_2016} & 1000(2050) &  &  & 7 (2050) &  & 1.08(2050) & \\
 & 400(2070) &  &  & 11 (2070) &  & 0.72(2070) & \\
Gas Reforming  & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 356.6 & 2022\\
\cite{iea_technology_2015,mehmeti_life_2018,keipi_economic_2018} & & & & & &  & \\
Gas Reforming-CCS(70\%) & 1200 & 8 & 0.065 & 30 & Eff=0.56 & 179 & 2022\\
\cite{iea_technology_2015,keipi_economic_2018,cormos_ana-maria_economic_2018} &  &  &  &  &  &  & \\
\gls{PEMFC} \cite{iea_technology_2015,simons_life-cycle_2015,kannan_life_2007} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.49 & 1.087(2022) & 2022\\
 & 4000(2030) &  &  &  &  & 0.65(2030) &  \\
 & 3000(2035) &  &  &  &  &  &  \\
\gls{SOFC} \cite{iea_technology_2015,simons_life-cycle_2015,rillo_life_2017,tu_advances_2004} & 7399(2030) & 30.65 & 0.59 & 10 (CF=0.9) & Eff=0.7 & 2.11(2030) & 2030\\
 & 4000(2035) &  &  &  &  & 1.27(2040) &  \\
 & 3000(2040) &  &  &  &  & &  \\
\gls{PWS} \cite{pinaud_technical_2013} & 14706  & 236.5 & 0 & 20(CF=0.9) & Eff=0.15(2050) & Unknown & 2050
\label{eco}
\end{longtable}
\end{landscape}

\begin{table}[!ht]
	\caption{Capacity limits.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth} }
		\hline
\textbf{Technology} & \textbf{Net Capacity} \textbf{Limit} (GW)\\
\hline
Photovoltaic \cite{isep_53_2018} & 332 \\
Onshore wind \cite{heger_wind_2016,kato_energy_2016} & 180 \\
Offshore wind (fixed) \cite{heger_wind_2016,kato_energy_2016}& 130 \\
Offshore wind (floating) \cite{heger_wind_2016,kato_energy_2016}& 260 \\
Nuclear & 50 (Scenarios 3 \& 4) \\
 & 100 (Scenario 2) \\
\gls{PWS} \cite{pinaud_technical_2013} & 100 (Scenario 5) \\
\hline 
\end{tabularx}
\label{caplim}
\end{table}

\begin{table}[!ht]
%\begin{minipage}{\textwidth} 
	\caption{Capacity growth rates.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
		\hline
\textbf{Technology} & \textbf{Max. Annual} \\
  & \textbf{Growth Rate}   \\
\hline
Nuclear (2027 onwards) & +5 reactors \\
Solar and Emerging Solar \cite{irena_renewable_2020} & 40\%  \\
Onshore Wind \cite{irena_renewable_2020} & 25\% \\
Offshore Wind(Fixed) \cite{irena_renewable_2020} & 20\% \\
Offshore Wind(Floating) \cite{irena_renewable_2020} & 20\% \\
Li-ion Storage & 30\% \\
Natural Gas &  50\% \\
\gls{USC} & 50\% \\
All emerging technologies & 40\% (Years 1-5) \\
& 60\% (Years 6-10) \\
 & 40\% (Years 11-15) \\
 & 30\% (Years 16-) \\
\hline 
\end{tabularx}
\label{growrate}
%\end{minipage}
\end{table}

\begin{table}[!ht]
	\caption{Miscellaneous model parameters and assumptions.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
		\hline
\textbf{Parameter} & \textbf{Value} \\
\hline
Currency & MUSD 2015 \\
Activity unit & GWh\\
Discount rate & 5\% \\
Transmission efficiency & 90 \% \\
Li-ion discharge time \cite{mongird_energy_2019} & 4h \\
Li-ion E/P ratio \cite{mongird_energy_2019} & 4  \\
Li-ion depth-of-discharge \cite{mongird_energy_2019} & 80\% \\
Li-ion lifetime cycles \cite{mongird_energy_2019} & 3500  \\
\hline 
	\end{tabularx}
\label{misc-assump}
\end{table}

### 2020-09-16 doc/2020-03-paper/litreview.tex
added final data references
Former-commit-id: 8768788b73a32289546225ccaa7e74028a3a5111
Former-commit-id: e84176721cdfaa57f6b7c10d5e92fde1a81dda1d

The Paris Agreement commits individual nations to significant carbon reduction over time through the Intended Nationally Determined Contribution (INDC) mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: by 2030, reduce GHG emissions by 26\% compared to 2013 levels, and by 2050, reduce overall GHG emissions by 80\% or more, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Cognizant of these targets, a number of authors have evaluated Japan's future energy system using a variety of modeling approaches. Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}. Recognizing the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency, Li et al. explored the role of hydrogen as a storage medium through \gls{P2G} approaches in Kyushu, Japan. Their study identified that \gls{P2G} can increase the effective utilization rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}. Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}. Considering Japan's economic conditions and demographic trends such as moderate GDP growth and rapid aging, Kuriyama et al. suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}. However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets. Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, cognizant of both CCS and nuclear deployment rates into the future. Consensus on policy options and priorities also has a large influence on modeling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}. A seminal work by Sugiyama et al. harmonizes a number of modeling approaches for Japan's long term (i.e. to the year 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models \cite{sugiyama_japans_2019}. Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction. Each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas. Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role \cite{sato_consideration_2005, akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}. Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}. Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight \gls{FCV}s and power generation, via both mixed and direct combustion. Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal fired power generation reduce toward 2050 \cite{ishimoto_significance_2017}. From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels which requires a three-fold reduction in cost by 2030, and further reductions into the future \cite{nagashima_japans_2018}. Under the Basic Hydrogen Strategy, the Japanese government aims to realize low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalize regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}. The strategy aims to account for both economic and geopolitical impacts and the need to prioritize research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}. A common thread across previous research is that the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred in response to the nuclear accident in 2011 \cite{oshiro_mid-century_2019}.

>>>>

The Paris Agreement commits individual nations to significant carbon reduction over time through the Intended Nationally Determined Contribution (INDC) mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: by 2030, reduce GHG emissions by 26\% compared to 2013 levels, and by 2050, reduce overall GHG emissions by 80\% or more, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Cognizant of these targets, a number of authors have evaluated Japan's future energy system using a variety of modeling approaches. Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}. Recognizing the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency, Li et al. explored the role of hydrogen as a storage medium through \gls{P2G} approaches in Kyushu, Japan. Their study identified that \gls{P2G} can increase the effective utilization rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}. Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}. Considering Japan's economic conditions and demographic trends such as moderate GDP growth and rapid aging, Kuriyama et al. suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}. However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets. Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, cognizant of both CCS and nuclear deployment rates into the future. Consensus on policy options and priorities also has a large influence on modeling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}. A seminal work by Sugiyama et al. harmonizes a number of modeling approaches for Japan's long term (i.e. to the year 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models \cite{sugiyama_japans_2019}. Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction. Each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas. Additionally, for Japan, the option for import of carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}. Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}. Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight \gls{FCV}s and power generation, via both mixed and direct combustion. Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal fired power generation reduce toward 2050 \cite{ishimoto_significance_2017}. From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels which requires a three-fold reduction in cost by 2030, and further reductions into the future \cite{nagashima_japans_2018}. Under the Basic Hydrogen Strategy, the Japanese government aims to realize low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalize regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}. The strategy aims to account for both economic and geopolitical impacts and the need to prioritize research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}. A common thread across previous research is that the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred in response to the nuclear accident in 2011 \cite{oshiro_mid-century_2019}.

### 2020-09-16 doc/2020-03-paper/methods.tex
added final data references
Former-commit-id: 8768788b73a32289546225ccaa7e74028a3a5111
Former-commit-id: e84176721cdfaa57f6b7c10d5e92fde1a81dda1d

%misc assumptions
Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively. Prices and projections for fossil fuels and nuclear fuel were incorporated (add references). Learning curves for costs and life-cycle emissions are compiled from existing data based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components. These learning curves are modelled as linear functions interpolated between the data values used, with the curve plateauing at the latest value for a given parameter, as detailed in Table \ref{eco}. Capacity limits of renewables and \gls{PWS} are based on their land-use requirements. The maximum annual capacity growth rates for existing technologies are held constant. The growth rate of nuclear power is based on historic trends and current pressure vessel manufacturing limitations. The reactor size assumed in this study is 1165 MWe. Due to a projected increase in the share of renewables, nuclear power plants must be able to load follow, which is simulated in our model based on French reactors' range of capacity factors. The growth rates of all emerging technologies are modeled on the rates observed for solar photovoltaic technology, with rapid initial growth followed by gradual reduction, eventually reaching a moderate maximum attainable growth rate. One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies. We believe that these technologies, some of which are already commercialized or close to commercialization, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain. Therefore, they could be deployed as rapidly as conventional solar photovoltaic.

All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load following. Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors (cite IEA). For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis. Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative, due to the rising cost of cobalt and nickel, and lithium-ion manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively (cite).

%approach, goal, what are we hoping to learn

>>>>

%misc assumptions
Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively. Prices and projections for fossil fuels and nuclear fuel were incorporated \cite{wittenstein_projected_2015, world_bank_group_commodity_2016, international_energy_agency_world_2019}. Learning curves for costs and life-cycle emissions are compiled from existing data based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components. These learning curves are modelled as linear functions interpolated between the data values used, with the curve plateauing at the latest value for a given parameter, as detailed in Table \ref{eco}. Capacity limits of renewables and \gls{PWS} are based on their land-use requirements. The maximum annual capacity growth rates for existing technologies are held constant. The growth rate of nuclear power is based on historic trends and current pressure vessel manufacturing limitations \cite{iaea_pris_nodate}. The reactor size assumed in this study is 1165 MWe. Due to a projected increase in the share of renewables, nuclear power plants must be able to load follow to a certain extent, which is simulated in a limited way in our model based on French reactors' range of capacity factors. The growth rates of all emerging technologies are modeled on the rates observed for solar photovoltaic technology, with rapid initial growth followed by gradual reduction, eventually reaching a moderate maximum attainable growth rate. One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies. We believe that these technologies, some of which are already commercialized or close to commercialization, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain. Therefore, they could be deployed as rapidly as conventional solar photovoltaic.

All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load following. Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}. For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis. Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative, due to the rising cost of cobalt and nickel, and lithium-ion manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.
